---
title: "p8105_hw5_anw2158"
author: "Aung Nay Win"
output: github_document
---

```{r, include=FALSE}
library(dplyr)
library(purrr)
library(ggplot2)
library(broom)
library(readr)
library(tidyr)
```

### Problem 1
## Description of The Raw Data

uid: A unique identifier for each homicide incident.
reported_date: The date on which the homicide was reported, in a YYYYMMDD format.
victim_last: The last name of the homicide victim.
victim_first: The first name of the homicide victim.
victim_race: The race of the victim.
victim_age: The age of the victim.
victim_sex: The sex of the victim, indicated as Male or Female.
city: The city where the homicide occurred.
state: The state where the homicide occurred.
lat: The latitude coordinate of the homicide location.
lon: The longitude coordinate of the homicide location.
disposition: The status of the case

```{r}
homicide_data = read_csv("./data/homicide-data.csv") |> 
  mutate(city_state = paste(city, state, sep = ", ")) |> 
  group_by(city_state) |> 
  summarise(total_homicides = n(),
            unsolved_homicides = sum(disposition %in% c("Closed without arrest", "Open/No arrest")))
```

Proportion Test for Baltimore, MD
```{r}
baltimore_data = homicide_data |>  filter(city_state == "Baltimore, MD")

prop_test_baltimore = 
  prop.test(baltimore_data$unsolved_homicides, baltimore_data$total_homicides)
tidy_baltimore = tidy(prop_test_baltimore)
```

Apply prop.test to Each City

```{r, warning=FALSE}
perform_tidy_prop_test = function(unsolved, total) {
  prop_test_result =  prop.test(unsolved, total)
  tidy(prop_test_result)
}

city_test_results = homicide_data |> 
  mutate(prop_test = pmap(list(unsolved_homicides, total_homicides), ~perform_tidy_prop_test(..1, ..2))) |> 
  unnest(prop_test)
```

```{r}
ggplot(city_test_results, aes(x = reorder(city_state, estimate), y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  coord_flip() +
  labs(x = "City", y = "Proportion of Unsolved Homicides") +
  theme_minimal()
```

